A comparison of the most popular AI text-to-image generation applications

### 2023-01-27 Paper.tex
Final changes

	\subsection{Context and background}
	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators. According to \citeauthor{whatIsTextToImageGen} (\citeyear{whatIsTextToImageGen}), text-to-image generators allow people to provide a text description which the generator then uses to produce images matching the description as closely as possible. This increase in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image). However, in our opinion it has also made the landscape more difficult to navigate because of its abundance of choice. This is illustrated by this article which shows that you would have to go through all of the models to find which is the best for each user as this author and most others all base their judgment on their own opinion (\cite{whyUseImageComp}). This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process in an objective way. This allows us to help people gain some perspective on which text-to-image generator is best for their needs.

@@

	We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting. According to \citeauthor{inpaintingExplaination} (\citeyear{inpaintingExplaination}), inpainting is an AI technique which allows a user to regenerate a missing part of an image. This allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result.

>>>>

	\subsection{Context and background}
	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators. Text-to-image generators allow people to provide a text description which the generator then uses to produce images matching the description as closely as possible (\cite{whatIsTextToImageGen}). This increase in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image). However, in our opinion it has also made the landscape more difficult to navigate because of its abundance of choice. This is illustrated by this article which shows that you would have to go through all of the models to find which is the best for each user as this author and most others all base their judgment on their own opinion (\cite{whyUseImageComp}). This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process in an objective way. This allows us to help people gain some perspective on which text-to-image generator is best for their needs.

@@

	We expect the best text-to-image generator out of the four we chose to be stable diffusion. This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting. Inpainting is an AI technique which allows a user to regenerate a missing part of an image (\cite{inpaintingExplaination}). This allows the user more freedom to fine-tune their result. Given enough time this will yield a more accurate result.
